### 2014-10-22 fundamentals/impl.tex
adds diagram

Agent-based modeling is inherently object oriented. Since agents are

The core of the simulator creates a set of key classes on which agent plugins 
are based. In addtion, a set of key tools are also provided to enrich the API 
and provide a robust suite of behaviors for the developer.

<diagram of core, modules, toolkit, etc>

Agent plugins utilize the generic core API to interact with one another.  For 
example, agents rely on the dynamic loading and paradigm for clean plugin 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

<diagram of black box facilities>

@@

A key innovation in \Cyclus is implementing this generic API and modular 
architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
common in modern software architecture, such a ``plugin'' pattern has 
previously not been implemented in nuclear fuel cycle simulators in the 
literature.  In \Cyclus, this implementation maximizes the potential of the clean, 
object-oriented \gls{API} and modern build system already described.

@@

Interchangability is accomplished by providing APIs that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{build} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power, 
very simply. The \gls{API} exposes \Class{Agent} helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

\begin{figure}[htbp!]
\begin{center}
\includegraphics{agent_uml}
\end{center}
\caption{The inheritance structure in the \Class{Agent} class abstracts away 
unneccesary details while exposing powerful functionality.}
\label{fig:agent_uml}
\end{figure}

@@

@@

\Cyclus implements a \gls{RIF} relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, RIF hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

@@

Although concept of the RIF hierarchy is provided, the \Cyclus kernel is
really designed to handle hierarchies of arbitrary depth.  It is just as easy
to run a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents' of regions.  By
convention, institutions are mainly responsible for facility deployment, but
any archetype can have access to \Cyclus' agent deployment mechanism.  It easy
to implement agents that deploy copies of themselves, or that schedule their
own decommissioning.  Because regions, institutions, and facilities are all
just agents, they can all be implemented to exercise the full set of features
offered by the \Cyclus kernel.

@@

TODO: add blurb about discrete agent/facility tracking.

@@

@@

\begin{figure}[htbp!]
\begin{center}
<diagram of a possible Cycamore-only simulation>
\end{center}
\caption{A simple once-through fuel cycle possible with only \Cycamore and 
\Cyclus.}
\label{fig:<+label+>}
\end{figure}<++>

>>>>

\acrlong{ABM} is inherently object-oriented. Since agents represent 
discrete, independently acting objects, object-orientation is the natural 
paradigm in which to conduct \gls{ABM}.

The core of the \Cyclus simulator creates a set of key classes on which agent plugins 
are based. In addtion, a set of key tools are also provided to enrich the 
\gls{API} and provide a robust suite of behaviors for the developer.

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\textwidth]{./images/framework}
\end{center}
\caption{The \Cyclus core provides \gls{API}s that abstract away the details in 
the kernel and allow the archetypes to be loaded into the simulation in a modular 
fashion.}
\label{fig:framework}
\end{figure}

Agent plugins utilize the generic core \gls{API} to interact with one another.  For 
example, agents rely on the dynamic loading and paradigm for clean plugin 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

@@

A key innovation in \Cyclus is implementing this generic \gls{API} and modular 
architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
common in modern software architecture, such a ``plugin'' pattern has 
previously not been implemented in nuclear fuel cycle simulators in the 
literature.  In \Cyclus, this implementation maximizes the potential of the clean, 
object-oriented \gls{API} and modern build system already described.

@@

Interchangability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{build} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power, 
very simply. The \gls{API} exposes \Class{Agent} helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./images/agent_uml}
\end{center}
\caption{The inheritance in \Cyclus classes, such as the \Class{Agent}, 
\Class{Facility}, \Class{Institution}, and \Class{Region} classes abstract away 
unneccesary details while exposing powerful functionality. In the above 
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in 
order to become a bonified Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}

@@

In this way, a researcher can directly compare two different reactor modeling 
implementations (perhaps \Class{DetailedReactor} and \Class{SimpleReactor} 
simply by exchanging the two corresponding archetypes. That is, two reactor 
archetypes, inheriting from the \Class{Facility} class, are indistinguishable 
from a simulation perspective. Two simulations, one using 
\Class{DetailedReactor} and the other using \Class{SimpleReactor} can therefore 
be compared directly to determine the impact of using one or the other model.
This can be done with any agent type, where agents can be ``Regions,'' 
``Institutions,'' or ``Facilities.''

@@

\Cyclus implements a \gls{RIF} relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

@@

Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
really designed to handle hierarchies of arbitrary depth.  It is just as easy
to run a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents' of regions.  By
convention, institutions are mainly responsible for facility deployment, but
any archetype can have access to \Cyclus' agent deployment mechanism.  It easy
to implement agents that deploy copies of themselves, or that schedule their
own decommissioning.  Because regions, institutions, and facilities are all
just agents, they can all be implemented to exercise the full set of features
offered by the \Cyclus kernel.

@@

\TODO{add blurb about discrete agent/facility tracking.}

@@

\subsubsection{Toolkit Extensions}

In addition to those that already exist, tools and computational patterns will 
emerge from the archetypes that are developed within the community of 
developers. As those tools gain adoption between projects and demonstrate their 
utility to the developer community, they will be considered for screening and 
adoption into the kernel as toolkit extensions. Likely extensions include:

\begin{itemize}
\item fuel cycle metrics calculators
\item supportive data tables
\item policy models
\item economic models
\item etc.
\end{itemize}

@@

\begin{figure}[htbp!]
\begin{center}
<diagram of a possible Cycamore-only simulation>
\end{center}
\caption{A simple once-through fuel cycle possible with only \Cycamore and 
\Cyclus.}
\label{fig:simplesim}
\end{figure}
